Diagnosing Child Poverty Reduction Interventions

### 2024-09-04 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Improvement to the density ridge line plots in diagnostics notebook

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
    geom_density_ridges() +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))

@@

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
    geom_density_ridges() +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))
  return(p)
}

>>>>

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
    geom_density_ridges(alpha = 0.3) +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))

@@

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source, fill = Source)) +
    geom_density_ridges(alpha = 0.3) +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))
  return(p)
}
